Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-11 paper.tex
Add shared origin example to fig.

\usepackage{booktabs}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{url}
% JK: turning this off for the moment as I keep clicking through on links
% to the bibliography while reading the text and it's intensely annoying.
% Can reinstate when we're ready to preprint
% \usepackage[hidelinks]{hyperref}

@@

The sequences of 14 Pango recombinants trace back to a single recombination
node. The details are given in Figure X, where we [give the details of
the numbers of samples, etc for each of these 14 lineages] and
show the lineage subgraph for X?, which makes this simple structure
clear. [Explain the lineage subgraph format a bit]

@@

>>>>

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{makecell}
\usepackage{url}
% JK: turning this off for the moment as I keep clicking through on links
% to the bibliography while reading the text and it's intensely annoying.
% Can reinstate when we're ready to preprint
% \usepackage[hidelinks]{hyperref}

@@

\begin{figure}
\begin{tabularx}{\textwidth}{cc}
\includegraphics[width=0.4\textwidth]{figures/Pango_XA_nxcld_tight_graph.pdf}
&
\begin{tabular}[b]{llr}
Lineage & number of samples & other details... \\
XA & & \\
XF & & \\
XG & & \\
XH & & \\
XL & & \\
XR & & \\
XT & & \\
XW & & \\
XY & & \\
XAC & & \\
XAE & & \\
XAK & & \\
XAA & & \\
XAB & & \\
XAG & & \\
\end{tabular}\\
\multicolumn{2}{c}{
\includegraphics[width=\textwidth]{figures/Pango_XAG_nxcld_tight_graph.pdf}}
\end{tabularx}
\caption{Single origin Pango X lineages. (A) Subgraph for XA (Wide ARG).
(B) Details for the the single-origin Pango
X lineages in the long ARG. (C) XAA, XAB and XAG share a single recombinant
origin in the Long ARG. }
\end{figure}

The sequences of 14 Pango recombinants trace back to a single recombination
node. The details are given in Figure X, where we [give the details of
the numbers of samples, etc for each of these 14 lineages] and
show the lineage subgraph for X?, which makes this simple structure
clear. [Explan the lineage subgraph format a bit]

@@

[Discuss panel C where XAA, XAB,XAG and share a common recombinant origin]
